MSD panels 1, 2 and 3 HVE Supernatant

### 2016-09-21 MSD_panels_1_2_3_HVE_sup_analysis.Rmd
formatting final plot

```{r  individual analyte plots, echo=FALSE,fig.width=8, fig.height = 10, message = FALSE, warning = FALSE}

ggplot(mergeMock, aes(x = Timepoint, y = MockSubtracted))+
   geom_jitter(aes(color = Donor), alpha = 0.75, size = 2.5, width = 0.2, height = 0.2)+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Analyte Concentrations by Donor, Timepoint and Condition")

>>>>

```{r  individual analyte plots, echo=FALSE,fig.width=8, fig.height = 15, message = FALSE, warning = FALSE}

ggplot(mergeMock, aes(x = Timepoint, y = MockSubtracted))+
   geom_jitter(aes(color = Donor), alpha = 0.75, size = 2.5, width = 0.2, height = 0.2)+
   labs( y = "log 10 Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))+
  ggtitle("Analyte Concentrations ")
